### 2025-07-30 getting-started.qmd
20250730 - updates

>>>>

## General Workflow {#sec-generalWorkflowAnalysis}

Here is a general workflow for statistical analysis:

1. Load the packages you need
1. Load the data files
1. Do any data processing needed to prepare the data files to be merged.
  - For example, make sure each data file has unique values on the keys.
1. Merge the data files
1. Do any data processing needed to prepare the data files for analysis.
For example:
  - calculate/recode variables
  - transform wide to long or long to wide
  - filter to the relevant rows
  - examine descriptive statistics to ensure data are plausible
- Do the analysis!
  - evaluate analysis assumptions
  - conduct sensitivity analyses to see extent to which findings differ using different subsets of the data, different modeling approaches/assumptions, etc.

### 2025-07-30 research-methods.qmd
20250730 - updates

@@

>>>>

## General Workflow {#sec-generalWorkflowStudy}

Here is a general workflow for a study:

1. Formulate your [research questions, hypotheses, resulting predictions, and exploratory questions](#sec-hypothesisVsPrediction)
1. Obtain approval from an institutional review board (IRB) to conduct the research
    - In the United States, analyzing publicly available data from `nflverse` is not considered human subjects research because the work is not considered to involve human subjects—the data involve publicly available information that is not sensitive (i.e., it does not pose risks to players' rights, privacy, or welfare), and the work does not involve intervention, interaction with the players, private information, or biospecimens.
1. Design the study to test your research questions
1. Collect the data you need to test your research questions
1. Analyze the data to test your research questions
1. Communicate the findings to others (e.g., papers, posters, talks, news articles, interviews, blog posts)

@@

Research questions that you do not have hypotheses and predictions for are considered exploratory questions.
Both hypothesis-driven work and exploration are important parts of science.
Just be honest about which one you are pursuing for each question.
Secretly hypothesizing after the results are known in the Introduction section of a paper (known as SHARKing) is problematic [@Hollenbeck2017].
Conducting many exploratory analyses is potentially more prone to false-positive results than conducting a single confirmatory (i.e., hypothesis-driven) test.
Thus, presenting exploratory work as confirmatory is misrepresenting the likelihood that your results are true and can contribute to the replication crisis—the failure of many findings from many studies to replicate upon subsequent investigation.
By contrast, it is fine to transparently hypothesize after the results are known in the Disucssion section of a paper (known as THARKing), because this can provide potential explanations for the findings that can be evaluated in subsequent analyses or studies [@Hollenbeck2017].
